% A complete, runnable LaTeX document for your resume
% This uses the moderncv class to create a clean, one-page layout.

% --- PREAMBLE ---
\documentclass[10pt, a4paper, sans]{moderncv} % Set base font size to 10pt
\moderncvstyle{banking} % 'banking' theme
\moderncvcolor{blue}    % You can change this to 'green', 'orange', 'red', etc.

% --- GEOMETRY ---
% Reduced margins to fit content on one page
\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=1.8cm, right=1.8cm]{geometry} 


% --- PERSONAL INFORMATION ---
\name{Vishal}{Shaji}
\title{Cloud \& DevOps} 

% CHANGE 1: Added \vspace{2.5mm} here to push the address down away from the Title
\address{\vspace{2.5mm}Kochi, India}{} 
\phone[mobile]{+91 7306997081}
\email{vishshaji03@gmail.com}

% Social links
\social[linkedin]{VishalShaji}
\social[github]{Vishhh03}



% --- THE DOCUMENT BEGINS ---
\begin{document}

% Configure hyperref for nice \url{} links
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=blue, % Make URLs blue and clickable
    pdftitle={Vishal Shaji - Resume},
    pdfpagemode=FullScreen,
}

\makecvtitle % Creates the header with your name and info

% CHANGE 2: Added negative space here to pull the Experience section UP
% Adjust -10mm to -5mm or -15mm to change the tightness
\vspace*{-10mm}

% --- Experience ---
\section{Experience}

\cventry
  {July 2025 -- Present} % Dates
  {Programmer Analyst Trainee} % Position
  {Cognizant Technology Solutions (CTS)} % Company
  {Chennai, India} % Location
  {} % Grade/Score (empty)
  {Led a 5-member team developing and modernizing a full-stack web platform while integrating DevOps practices.
  \begin{itemize}%
    \item Developed Smart Hotel Management System (Angular + .NET + SQL Server).
    \item Performed primary pull request reviews and maintained the remote Git repository.
    \item Containerized the application using Docker and implemented Github Actions-based CI/CD pipeline.
    \item Integrated Prometheus \& Grafana for live monitoring and ELK Stack for log management.
  \end{itemize}}

\vspace{2mm} % Added space between job entries

\cventry
  {Jan 2025 -- June 2025} % Dates
  {Tech Consultant (Intern)} % Position
  {Bommaku Constructions} % Company
  {Hyderabad, India} % Location
  {} % Grade/Score (empty)
  {Supported the company's digital transformation and modernization through web, cloud, and visualization solutions.
  \begin{itemize}%
    \item Optimized website performance and provided UI/UX enhancement suggestions.
    \item Designed Unreal Engine 5 architectural visualization for construction projects.
    \item Guided the management team on adopting cloud technologies for operational efficiency.
  \end{itemize}}
% --- Projects ---
\section{Projects}

\cventry
  {} % Dates (empty)
  {Cloud DevOps Live Project} % Project Name
  {TerraLess - Stateless Server Hosting} % Company
  {} % Location (empty)
  {} % Grade/Score (empty)
  {A production-grade platform for on-demand game server hosting, reducing costs by 90\% via ephemeral architecture.
  \begin{itemize}%
    \item Architected a "Stateless" computing model using Hetzner Cloud and Btrfs snapshots to decouple data from compute.
    \item Developed a modern Next.js frontend with AWS Amplify authentication, featuring real-time cost transparency.
    \item Automated complex lifecycle workflows (Provision $\rightarrow$ Rehydrate $\rightarrow$ Snapshot $\rightarrow$ Destroy) using Bash and Cloud APIs.
    \item Integrating NVMe storage with Storage Box for instant, atomic offsite backups and 1TB+ data retention.
  \end{itemize}
  \textit{Live Site: \url{www.terraless.com}}}

\vspace{2mm} % Added space between project entries

\cventry
  {} % Dates (empty)
  {Client Website Deployment (Next.js + Sanity CMS)} % Project Name
  {Idha Art Stay} % Company
  {} % Location (empty)
  {} % Grade/Score (empty)
  {Deployed a production-grade client website with automated build pipelines and CMS integration.
  \begin{itemize}%
    \item Built a responsive Next.js + Sanity CMS frontend for an art homestay business.
    \item Set up CI/CD pipelines using GitHub Actions for deployment to Cloudflare.
    \item Configured Cloudflare CDN for performance optimization and SEO improvements.
  \end{itemize}
  \textit{Live Site: \url{www.idhafortkochi.com}}}

% --- Education ---
\section{Education}

\cventry
  {2019 -- 2023} % Dates
  {Bachelor of Technology (B.Tech) - Civil Engineering (Minor in ML)} % Degree
  {TOCH Institute of Science and Technology} % Institution
  {Kochi, India} % Location
  {} % Grade
  {
  \begin{itemize}%
    \item Led ML-based civil data analysis (Kochi Metro Analysis) final year project.
  \end{itemize}}

\cventry
  {2017 -- 2019} % Dates
  {Higher Secondary Education - Computer Science Stream} % Degree
  {Gregorian Public School} % Institution
  {Kochi, India} % Location
  {} % Grade
  {} % Description

% --- Technical Skills ---
\section{Technical Skills}

\cvitem{DevOps \& Cloud}{AWS (EC2, Lambda, IAM, S3, CloudWatch, ECS, SNS, Cognito), Docker, Jenkins, Terraform, GitHub Actions, Prometheus, Grafana, ELK Stack, Bash Scripting, Git, GitHub}
\cvitem{Programming}{Python, JavaScript, C\#, SQL}
\cvitem{Web Development}{Angular, .NET Core, Next.js, React, FastAPI, Headless CMS, Cloudflare, DNS Configuration}
\cvitem{Databases}{PostgreSQL, SQL Server, DynamoDB, MongoDB, RDS}
\cvitem{Operating Systems}{Linux (Ubuntu, Amazon Linux)}

% --- Certificates ---
\section{Certifications}

\cvitem{2024}{AWS Certified Cloud Practitioner}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Foundational Associate}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Foundational AI}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Associate Architect}

\end{document}